### 2024-10-06 common/characteristic.tex

        \printbibliography[heading=nobibheading, section=1, env=countauthorvak,          keyword=biblioauthorvak]%

@@

        \printbibliography[heading=nobibheading, section=1, env=countauthorscopuswos,    filter=scopuswos]%

>>>>

        \phantom{\printbibliography[heading=nobibheading, section=1, env=countauthorvak,          keyword=biblioauthorvak]%

@@

        \printbibliography[heading=nobibheading, section=1, env=countauthorscopuswos,    filter=scopuswos]}%
